oREV: an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children

### 2022-11-04 analysis/item_selection.Rmd
clean repo
add rasch based selected items

---
title: "CLT item selection"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
```

```{r}
data <- read_csv("../data/clt_clean_data.csv")%>%
  filter(age_group != 8)

@@

# params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
#   select(-uci, -lci)%>%
#   pivot_wider(names_from = order, values_from = mode)%>%
#   mutate(order_dif = A-B)
```

# Differential item functioning

@@

>>>>

---
title: "oREV item selection"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r}
data <- read_csv("../data/clean_data.csv")

irt_dat <- data%>%
  select(subjID, targetWord, correct, order, sex, aoa_german_comb)

@@

# params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
#   select(-uci, -lci)%>%
#   pivot_wider(names_from = order, values_from = mode)%>%
#   mutate(order_dif = A-B)
```
# Item selection based on 3PL model

## Differential item functioning

@@

# Item selection based on Rasch Model

```{r}
irt1 <- readRDS("../saves/irt1.rds")

rasch_fit <- irt_dat%>%
  select(-order, -sex)%>%
  filter(#targetWord %in% c("door", "jaguar","zucchini"),
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

rasch_fit_mode <- rasch_fit%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  group_by(targetWord, fit_index)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))

rasch_sel_items <- rasch_fit_mode%>%
  select(-lci, -uci)%>%
  pivot_wider(names_from = fit_index, values_from = mode)%>%
  filter(0.5 < infit & 1.5 > infit,
         0.5 < outfit & 1.5 > outfit)%>%
  pull(targetWord)

saveRDS(rasch_sel_items, "../saves/rasch_selected_items.rds")
```

```{r}
rasch_fit%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  #facet_grid(~fit_index)+
  xlim(0,10)+
  theme_bw()
```

### 2022-11-04 paper/manuscript.Rmd
add rasch based selected items

>>>>

# Open Practices Statement

The task can be accessed via the following website: https://ccp-odc.eva.mpg.de/orev-demo/. The corresponding source code can be found in the following repository: https://github.com/ccp-eva/orev-demo. The data sets generated during and/or analysed during the current study are available in the following repository: https://ccp-odc.eva.mpg.de/orev-demo/. Data collection was preregistered at: https://osf.io/qzstk.

### 2022-11-04 paper/manuscript.tex
add rasch based selected items

>>>>

\hypertarget{open-practices-statement}{%
\section{Open Practices Statement}\label{open-practices-statement}}

The task can be accessed via the following website: \url{https://ccp-odc.eva.mpg.de/orev-demo/}. The corresponding source code can be found in the following repository: \url{https://github.com/ccp-eva/orev-demo}. The data sets generated during and/or analysed during the current study are available in the following repository: \url{https://ccp-odc.eva.mpg.de/orev-demo/}. Data collection was preregistered at: \url{https://osf.io/qzstk}.
